### 2020-03-09 figheatmap_R0_03.tex
new figures!!!!!!

% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:45
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
	(338.79, 44.28);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
	(338.79, 71.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
	(338.79, 98.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
	(338.79,125.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
	(338.79,153.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
	(338.79,180.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
	(338.79,207.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
	(338.79,234.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
	(338.79,261.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
	(338.79,288.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
	(110.31,302.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
	(262.63,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(338.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
	(338.79, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
	(338.79, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
	(338.79,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
	(338.79,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
	(338.79,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
	(338.79,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
	(338.79,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
	(338.79,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
	(338.79,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
	(338.79,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
	(186.47,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
	(338.79,302.56);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.72) {
	\pgfimage[width=303.25pt,height=267.79pt,interpolate=false]{figheatmap_R0_03_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,189.02) --
	( 34.89,189.73) --
	( 36.28,191.09) --
	( 36.35,191.16) --
	( 37.64,192.45) --
	( 38.55,193.38) --
	( 38.97,193.81) --
	( 40.28,195.17) --
	( 40.75,195.66) --
	( 41.57,196.53) --
	( 42.83,197.89) --
	( 42.95,198.01) --
	( 44.07,199.25) --
	( 45.14,200.44) --
	( 45.29,200.61) --
	( 46.48,201.97) --
	( 47.34,202.95) --
	( 47.66,203.32) --
	( 48.81,204.68) --
	( 49.54,205.55) --
	( 49.95,206.04) --
	( 51.06,207.40) --
	( 51.74,208.23) --
	( 52.16,208.76) --
	( 53.24,210.12) --
	( 53.93,211.01) --
	( 54.30,211.48) --
	( 55.34,212.84) --
	( 56.13,213.88) --
	( 56.37,214.20) --
	( 57.37,215.56) --
	( 58.33,216.86) --
	( 58.37,216.92) --
	( 59.34,218.28) --
	( 60.31,219.64) --
	( 60.53,219.95) --
	( 61.25,221.00) --
	( 62.19,222.36) --
	( 62.72,223.14) --
	( 63.11,223.71) --
	( 64.01,225.07) --
	( 64.90,226.43) --
	( 64.92,226.46) --
	( 65.78,227.79) --
	( 66.64,229.15) --
	( 67.12,229.91) --
	( 67.49,230.51) --
	( 68.33,231.87) --
	( 69.16,233.23) --
	( 69.32,233.48) --
	( 69.98,234.59) --
	( 70.78,235.95) --
	( 71.51,237.20) --
	( 71.57,237.31) --
	( 72.35,238.67) --
	( 73.12,240.03) --
	( 73.71,241.07) --
	( 73.88,241.39) --
	( 74.63,242.75) --
	( 75.37,244.11) --
	( 75.91,245.10) --
	( 76.10,245.46) --
	( 76.82,246.82) --
	( 77.53,248.18) --
	( 78.11,249.29) --
	( 78.23,249.54) --
	( 78.92,250.90) --
	( 79.60,252.26) --
	( 80.28,253.62) --
	( 80.30,253.67) --
	( 80.94,254.98) --
	( 81.60,256.34) --
	( 82.25,257.70) --
	( 82.50,258.23) --
	( 82.89,259.06) --
	( 83.52,260.42) --
	( 84.14,261.78) --
	( 84.70,263.00) --
	( 84.76,263.14) --
	( 85.37,264.50) --
	( 85.97,265.86) --
	( 86.56,267.21) --
	( 86.90,267.98) --
	( 87.15,268.57) --
	( 87.73,269.93) --
	( 88.30,271.29) --
	( 88.87,272.65) --
	( 89.09,273.19) --
	( 89.43,274.01) --
	( 89.98,275.37) --
	( 90.53,276.73) --
	( 91.07,278.09) --
	( 91.29,278.65) --
	( 91.60,279.45) --
	( 92.13,280.81) --
	( 92.65,282.17) --
	( 93.17,283.53) --
	( 93.49,284.37) --
	( 93.68,284.89) --
	( 94.18,286.25) --
	( 94.68,287.60) --
	( 95.18,288.96) --
	( 95.67,290.32) --
	( 95.69,290.38) --
	( 96.15,291.68) --
	( 96.62,293.04) --
	( 97.10,294.40) --
	( 97.57,295.76) --
	( 97.88,296.69) --
	( 98.03,297.12) --
	( 98.48,298.48) --
	( 98.94,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 63.05) --
	( 35.49, 63.31) --
	( 36.35, 63.48) --
	( 38.55, 63.94) --
	( 40.75, 64.40) --
	( 41.98, 64.67) --
	( 42.95, 64.88) --
	( 45.14, 65.38) --
	( 47.34, 65.89) --
	( 47.91, 66.03) --
	( 49.54, 66.42) --
	( 51.74, 66.97) --
	( 53.35, 67.39) --
	( 53.93, 67.54) --
	( 56.13, 68.13) --
	( 58.33, 68.74) --
	( 58.37, 68.75) --
	( 60.53, 69.37) --
	( 62.72, 70.02) --
	( 63.01, 70.11) --
	( 64.92, 70.70) --
	( 67.12, 71.40) --
	( 67.32, 71.47) --
	( 69.32, 72.13) --
	( 71.32, 72.83) --
	( 71.51, 72.89) --
	( 73.71, 73.68) --
	( 75.06, 74.19) --
	( 75.91, 74.51) --
	( 78.11, 75.36) --
	( 78.55, 75.54) --
	( 80.30, 76.26) --
	( 81.83, 76.90) --
	( 82.50, 77.19) --
	( 84.70, 78.17) --
	( 84.91, 78.26) --
	( 86.90, 79.18) --
	( 87.81, 79.62) --
	( 89.09, 80.25) --
	( 90.55, 80.98) --
	( 91.29, 81.36) --
	( 93.13, 82.34) --
	( 93.49, 82.53) --
	( 95.58, 83.70) --
	( 95.69, 83.76) --
	( 97.88, 85.05) --
	( 97.90, 85.06) --
	(100.08, 86.41) --
	(100.10, 86.42) --
	(102.19, 87.78) --
	(102.28, 87.83) --
	(104.19, 89.14) --
	(104.47, 89.34) --
	(106.08, 90.50) --
	(106.67, 90.93) --
	(107.90, 91.86) --
	(108.87, 92.61) --
	(109.63, 93.22) --
	(111.07, 94.40) --
	(111.28, 94.58) --
	(112.87, 95.94) --
	(113.26, 96.29) --
	(114.38, 97.29) --
	(115.46, 98.30) --
	(115.84, 98.65) --
	(117.24,100.01) --
	(117.66,100.43) --
	(118.58,101.37) --
	(119.86,102.72) --
	(119.87,102.73) --
	(121.11,104.09) --
	(122.05,105.16) --
	(122.31,105.45) --
	(123.46,106.81) --
	(124.25,107.77) --
	(124.58,108.17) --
	(125.65,109.53) --
	(126.45,110.58) --
	(126.68,110.89) --
	(127.68,112.25) --
	(128.65,113.60) --
	(128.65,113.61) --
	(129.59,114.97) --
	(130.50,116.33) --
	(130.84,116.86) --
	(131.37,117.68) --
	(132.22,119.04) --
	(133.04,120.39) --
	(133.05,120.40) --
	(133.85,121.76) --
	(134.62,123.12) --
	(135.24,124.23) --
	(135.38,124.48) --
	(136.11,125.84) --
	(136.82,127.20) --
	(137.44,128.42) --
	(137.51,128.56) --
	(138.18,129.92) --
	(138.83,131.28) --
	(139.47,132.64) --
	(139.63,133.00) --
	(140.09,134.00) --
	(140.69,135.36) --
	(141.28,136.72) --
	(141.83,138.03) --
	(141.85,138.08) --
	(142.41,139.43) --
	(142.95,140.79) --
	(143.48,142.15) --
	(144.00,143.51) --
	(144.03,143.59) --
	(144.50,144.87) --
	(145.00,146.23) --
	(145.48,147.59) --
	(145.95,148.95) --
	(146.23,149.76) --
	(146.41,150.31) --
	(146.86,151.67) --
	(147.30,153.03) --
	(147.73,154.39) --
	(148.15,155.75) --
	(148.42,156.65) --
	(148.56,157.11) --
	(148.96,158.47) --
	(149.36,159.83) --
	(149.74,161.18) --
	(150.12,162.54) --
	(150.49,163.90) --
	(150.62,164.38) --
	(150.86,165.26) --
	(151.21,166.62) --
	(151.56,167.98) --
	(151.90,169.34) --
	(152.24,170.70) --
	(152.57,172.06) --
	(152.82,173.12) --
	(152.89,173.42) --
	(153.20,174.78) --
	(153.51,176.14) --
	(153.82,177.50) --
	(154.12,178.86) --
	(154.41,180.22) --
	(154.70,181.57) --
	(154.98,182.93) --
	(155.02,183.09) --
	(155.26,184.29) --
	(155.53,185.65) --
	(155.80,187.01) --
	(156.06,188.37) --
	(156.32,189.73) --
	(156.58,191.09) --
	(156.83,192.45) --
	(157.08,193.81) --
	(157.21,194.57) --
	(157.32,195.17) --
	(157.56,196.53) --
	(157.79,197.89) --
	(158.02,199.25) --
	(158.25,200.61) --
	(158.47,201.97) --
	(158.69,203.32) --
	(158.91,204.68) --
	(159.12,206.04) --
	(159.33,207.40) --
	(159.41,207.91) --
	(159.54,208.76) --
	(159.74,210.12) --
	(159.94,211.48) --
	(160.14,212.84) --
	(160.33,214.20) --
	(160.53,215.56) --
	(160.71,216.92) --
	(160.90,218.28) --
	(161.09,219.64) --
	(161.27,221.00) --
	(161.45,222.36) --
	(161.61,223.61) --
	(161.62,223.71) --
	(161.79,225.07) --
	(161.96,226.43) --
	(162.13,227.79) --
	(162.30,229.15) --
	(162.46,230.51) --
	(162.62,231.87) --
	(162.78,233.23) --
	(162.94,234.59) --
	(163.10,235.95) --
	(163.25,237.31) --
	(163.40,238.67) --
	(163.55,240.03) --
	(163.70,241.39) --
	(163.81,242.37) --
	(163.85,242.75) --
	(163.99,244.11) --
	(164.13,245.46) --
	(164.27,246.82) --
	(164.41,248.18) --
	(164.54,249.54) --
	(164.68,250.90) --
	(164.81,252.26) --
	(164.94,253.62) --
	(165.07,254.98) --
	(165.20,256.34) --
	(165.33,257.70) --
	(165.46,259.06) --
	(165.58,260.42) --
	(165.70,261.78) --
	(165.83,263.14) --
	(165.95,264.50) --
	(166.00,265.15) --
	(166.06,265.86) --
	(166.18,267.21) --
	(166.30,268.57) --
	(166.41,269.93) --
	(166.52,271.29) --
	(166.63,272.65) --
	(166.74,274.01) --
	(166.85,275.37) --
	(166.96,276.73) --
	(167.07,278.09) --
	(167.17,279.45) --
	(167.28,280.81) --
	(167.38,282.17) --
	(167.48,283.53) --
	(167.59,284.89) --
	(167.69,286.25) --
	(167.79,287.60) --
	(167.88,288.96) --
	(167.98,290.32) --
	(168.08,291.68) --
	(168.17,293.04) --
	(168.20,293.43) --
	(168.27,294.40) --
	(168.36,295.76) --
	(168.45,297.12) --
	(168.54,298.48) --
	(168.63,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 87.12) --
	(335.33, 87.78) --
	(335.21, 87.82) --
	(333.01, 88.53) --
	(331.22, 89.14) --
	(330.81, 89.28) --
	(328.62, 90.04) --
	(327.34, 90.50) --
	(326.42, 90.83) --
	(324.22, 91.65) --
	(323.68, 91.86) --
	(322.02, 92.50) --
	(320.22, 93.22) --
	(319.83, 93.38) --
	(317.63, 94.28) --
	(316.94, 94.58) --
	(315.43, 95.23) --
	(313.83, 95.94) --
	(313.23, 96.20) --
	(311.04, 97.22) --
	(310.87, 97.29) --
	(308.84, 98.27) --
	(308.05, 98.65) --
	(306.64, 99.36) --
	(305.37,100.01) --
	(304.44,100.49) --
	(302.80,101.37) --
	(302.25,101.67) --
	(300.35,102.73) --
	(300.05,102.90) --
	(298.01,104.09) --
	(297.85,104.18) --
	(295.76,105.45) --
	(295.65,105.52) --
	(293.61,106.81) --
	(293.46,106.91) --
	(291.54,108.17) --
	(291.26,108.36) --
	(289.55,109.53) --
	(289.06,109.87) --
	(287.64,110.89) --
	(286.86,111.46) --
	(285.81,112.25) --
	(284.67,113.12) --
	(284.04,113.61) --
	(282.47,114.85) --
	(282.33,114.97) --
	(280.68,116.33) --
	(280.27,116.67) --
	(279.10,117.68) --
	(278.07,118.58) --
	(277.56,119.04) --
	(276.08,120.40) --
	(275.88,120.59) --
	(274.64,121.76) --
	(273.68,122.70) --
	(273.26,123.12) --
	(271.91,124.48) --
	(271.48,124.93) --
	(270.61,125.84) --
	(269.35,127.20) --
	(269.28,127.27) --
	(268.13,128.56) --
	(267.09,129.75) --
	(266.94,129.92) --
	(265.79,131.28) --
	(264.89,132.37) --
	(264.67,132.64) --
	(263.58,134.00) --
	(262.69,135.14) --
	(262.52,135.36) --
	(261.50,136.72) --
	(260.50,138.08) --
	(260.49,138.08) --
	(259.52,139.43) --
	(258.58,140.79) --
	(258.30,141.20) --
	(257.65,142.15) --
	(256.75,143.51) --
	(256.10,144.53) --
	(255.88,144.87) --
	(255.02,146.23) --
	(254.19,147.59) --
	(253.90,148.07) --
	(253.38,148.95) --
	(252.58,150.31) --
	(251.81,151.67) --
	(251.70,151.86) --
	(251.05,153.03) --
	(250.31,154.39) --
	(249.59,155.75) --
	(249.51,155.91) --
	(248.89,157.11) --

>>>>

% Created by tikzDevice version 0.12.3 on 2020-03-09 13:22:38
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (302.65,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (302.65,266.42);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 42.47) --
	(302.65, 42.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 66.05) --
	(302.65, 66.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 89.62) --
	(302.65, 89.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,113.19) --
	(302.65,113.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,136.77) --
	(302.65,136.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,160.34) --
	(302.65,160.34);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,183.91) --
	(302.65,183.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.49) --
	(302.65,207.49);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,231.06) --
	(302.65,231.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,254.64) --
	(302.65,254.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.28, 30.69) --
	(101.28,266.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] (235.53, 30.69) --
	(235.53,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(302.65, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 54.26) --
	(302.65, 54.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 77.83) --
	(302.65, 77.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,101.41) --
	(302.65,101.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,124.98) --
	(302.65,124.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,148.55) --
	(302.65,148.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,172.13) --
	(302.65,172.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,195.70) --
	(302.65,195.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,219.28) --
	(302.65,219.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,242.85) --
	(302.65,242.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,266.42) --
	(302.65,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 30.69) --
	(168.41,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 30.69) --
	(302.65,266.42);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.12,  32.45) {
	\pgfimage[width=267.28pt,height=232.20pt,interpolate=false]{figheatmap_R0_03_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,167.98) --
	( 34.80,168.59) --
	( 36.03,169.77) --
	( 36.09,169.83) --
	( 37.22,170.95) --
	( 38.03,171.75) --
	( 38.40,172.13) --
	( 39.56,173.31) --
	( 39.97,173.73) --
	( 40.69,174.49) --
	( 41.80,175.66) --
	( 41.90,175.77) --
	( 42.89,176.84) --
	( 43.84,177.88) --
	( 43.97,178.02) --
	( 45.02,179.20) --
	( 45.78,180.06) --
	( 46.06,180.38) --
	( 47.07,181.56) --
	( 47.71,182.31) --
	( 48.07,182.74) --
	( 49.06,183.91) --
	( 49.65,184.64) --
	( 50.02,185.09) --
	( 50.97,186.27) --
	( 51.59,187.04) --
	( 51.91,187.45) --
	( 52.83,188.63) --
	( 53.52,189.54) --
	( 53.73,189.81) --
	( 54.62,190.99) --
	( 55.46,192.12) --
	( 55.50,192.17) --
	( 56.36,193.34) --
	( 57.21,194.52) --
	( 57.40,194.79) --
	( 58.04,195.70) --
	( 58.86,196.88) --
	( 59.33,197.56) --
	( 59.67,198.06) --
	( 60.47,199.24) --
	( 61.26,200.42) --
	( 61.27,200.44) --
	( 62.03,201.60) --
	( 62.79,202.77) --
	( 63.21,203.43) --
	( 63.54,203.95) --
	( 64.28,205.13) --
	( 65.01,206.31) --
	( 65.14,206.53) --
	( 65.73,207.49) --
	( 66.43,208.67) --
	( 67.08,209.75) --
	( 67.14,209.85) --
	( 67.82,211.02) --
	( 68.50,212.20) --
	( 69.02,213.11) --
	( 69.17,213.38) --
	( 69.83,214.56) --
	( 70.48,215.74) --
	( 70.96,216.60) --
	( 71.13,216.92) --
	( 71.76,218.10) --
	( 72.38,219.28) --
	( 72.89,220.24) --
	( 73.00,220.45) --
	( 73.61,221.63) --
	( 74.21,222.81) --
	( 74.81,223.99) --
	( 74.83,224.03) --
	( 75.39,225.17) --
	( 75.97,226.35) --
	( 76.54,227.53) --
	( 76.77,227.99) --
	( 77.11,228.70) --
	( 77.66,229.88) --
	( 78.21,231.06) --
	( 78.70,232.12) --
	( 78.76,232.24) --
	( 79.29,233.42) --
	( 79.82,234.60) --
	( 80.35,235.78) --
	( 80.64,236.44) --
	( 80.86,236.96) --
	( 81.37,238.13) --
	( 81.88,239.31) --
	( 82.38,240.49) --
	( 82.58,240.96) --
	( 82.87,241.67) --
	( 83.36,242.85) --
	( 83.84,244.03) --
	( 84.32,245.21) --
	( 84.51,245.69) --
	( 84.79,246.39) --
	( 85.25,247.56) --
	( 85.71,248.74) --
	( 86.17,249.92) --
	( 86.45,250.65) --
	( 86.62,251.10) --
	( 87.06,252.28) --
	( 87.50,253.46) --
	( 87.94,254.64) --
	( 88.37,255.81) --
	( 88.39,255.86) --
	( 88.79,256.99) --
	( 89.21,258.17) --
	( 89.63,259.35) --
	( 90.04,260.53) --
	( 90.32,261.33) --
	( 90.45,261.71) --
	( 90.85,262.89) --
	( 91.25,264.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 58.75) --
	( 35.33, 58.97) --
	( 36.09, 59.12) --
	( 38.03, 59.52) --
	( 39.97, 59.92) --
	( 41.05, 60.15) --
	( 41.90, 60.34) --
	( 43.84, 60.77) --
	( 45.78, 61.21) --
	( 46.28, 61.33) --
	( 47.71, 61.67) --
	( 49.65, 62.15) --
	( 51.08, 62.51) --
	( 51.59, 62.64) --
	( 53.52, 63.15) --
	( 55.46, 63.68) --
	( 55.50, 63.69) --
	( 57.40, 64.23) --
	( 59.33, 64.79) --
	( 59.59, 64.87) --
	( 61.27, 65.38) --
	( 63.21, 65.99) --
	( 63.38, 66.05) --
	( 65.14, 66.63) --
	( 66.91, 67.23) --
	( 67.08, 67.28) --
	( 69.02, 67.97) --
	( 70.21, 68.40) --
	( 70.96, 68.68) --
	( 72.89, 69.43) --
	( 73.29, 69.58) --
	( 74.83, 70.20) --
	( 76.18, 70.76) --
	( 76.77, 71.01) --
	( 78.70, 71.85) --
	( 78.89, 71.94) --
	( 80.64, 72.74) --
	( 81.45, 73.12) --
	( 82.58, 73.66) --
	( 83.86, 74.30) --
	( 84.51, 74.63) --
	( 86.14, 75.48) --
	( 86.45, 75.64) --
	( 88.29, 76.65) --
	( 88.39, 76.71) --
	( 90.32, 77.82) --
	( 90.34, 77.83) --
	( 92.26, 79.00) --
	( 92.28, 79.01) --
	( 94.12, 80.19) --
	( 94.20, 80.24) --
	( 95.88, 81.37) --
	( 96.13, 81.55) --
	( 97.55, 82.55) --
	( 98.07, 82.92) --
	( 99.15, 83.73) --
	(100.01, 84.38) --
	(100.67, 84.91) --
	(101.94, 85.93) --
	(102.13, 86.08) --
	(103.53, 87.26) --
	(103.88, 87.57) --
	(104.87, 88.44) --
	(105.82, 89.31) --
	(106.15, 89.62) --
	(107.38, 90.80) --
	(107.75, 91.16) --
	(108.57, 91.98) --
	(109.69, 93.14) --
	(109.70, 93.16) --
	(110.80, 94.33) --
	(111.63, 95.26) --
	(111.85, 95.51) --
	(112.87, 96.69) --
	(113.57, 97.52) --
	(113.85, 97.87) --
	(114.80, 99.05) --
	(115.50, 99.96) --
	(115.71,100.23) --
	(116.59,101.41) --
	(117.44,102.58) --
	(117.44,102.59) --
	(118.27,103.76) --
	(119.07,104.94) --
	(119.38,105.41) --
	(119.84,106.12) --
	(120.59,107.30) --
	(121.31,108.47) --
	(121.32,108.48) --
	(122.02,109.66) --
	(122.70,110.84) --
	(123.25,111.80) --
	(123.37,112.02) --
	(124.01,113.19) --
	(124.64,114.37) --
	(125.19,115.43) --
	(125.25,115.55) --
	(125.84,116.73) --
	(126.41,117.91) --
	(126.98,119.09) --
	(127.12,119.40) --
	(127.52,120.27) --
	(128.05,121.44) --
	(128.57,122.62) --
	(129.06,123.77) --
	(129.07,123.80) --
	(129.57,124.98) --
	(130.04,126.16) --
	(130.51,127.34) --
	(130.97,128.52) --
	(131.00,128.59) --
	(131.41,129.70) --
	(131.85,130.87) --
	(132.27,132.05) --
	(132.69,133.23) --
	(132.93,133.93) --
	(133.10,134.41) --
	(133.49,135.59) --
	(133.88,136.77) --
	(134.26,137.95) --
	(134.63,139.12) --
	(134.87,139.90) --
	(134.99,140.30) --
	(135.35,141.48) --
	(135.69,142.66) --
	(136.03,143.84) --
	(136.37,145.02) --
	(136.69,146.20) --
	(136.81,146.61) --
	(137.01,147.38) --
	(137.33,148.55) --
	(137.63,149.73) --
	(137.93,150.91) --
	(138.23,152.09) --
	(138.52,153.27) --
	(138.74,154.19) --
	(138.80,154.45) --
	(139.08,155.63) --
	(139.36,156.81) --
	(139.62,157.98) --
	(139.89,159.16) --
	(140.15,160.34) --
	(140.40,161.52) --
	(140.65,162.70) --
	(140.68,162.84) --
	(140.90,163.88) --
	(141.14,165.06) --
	(141.37,166.23) --
	(141.60,167.41) --
	(141.83,168.59) --
	(142.06,169.77) --
	(142.28,170.95) --
	(142.50,172.13) --
	(142.62,172.78) --
	(142.71,173.31) --
	(142.92,174.49) --
	(143.13,175.66) --
	(143.33,176.84) --
	(143.53,178.02) --
	(143.73,179.20) --
	(143.92,180.38) --
	(144.11,181.56) --
	(144.30,182.74) --
	(144.49,183.91) --
	(144.55,184.35) --
	(144.67,185.09) --
	(144.85,186.27) --
	(145.02,187.45) --
	(145.20,188.63) --
	(145.37,189.81) --
	(145.54,190.99) --
	(145.70,192.17) --
	(145.87,193.34) --
	(146.03,194.52) --
	(146.19,195.70) --
	(146.35,196.88) --
	(146.49,197.97) --
	(146.50,198.06) --
	(146.65,199.24) --
	(146.80,200.42) --
	(146.95,201.60) --
	(147.10,202.77) --
	(147.24,203.95) --
	(147.39,205.13) --
	(147.53,206.31) --
	(147.66,207.49) --
	(147.80,208.67) --
	(147.94,209.85) --
	(148.07,211.02) --
	(148.20,212.20) --
	(148.33,213.38) --
	(148.43,214.23) --
	(148.46,214.56) --
	(148.59,215.74) --
	(148.71,216.92) --
	(148.84,218.10) --
	(148.96,219.28) --
	(149.08,220.45) --
	(149.20,221.63) --
	(149.31,222.81) --
	(149.43,223.99) --
	(149.55,225.17) --
	(149.66,226.35) --
	(149.77,227.53) --
	(149.88,228.70) --
	(149.99,229.88) --
	(150.10,231.06) --
	(150.21,232.24) --
	(150.31,233.42) --
	(150.36,233.99) --
	(150.42,234.60) --
	(150.52,235.78) --
	(150.62,236.96) --
	(150.72,238.13) --
	(150.82,239.31) --
	(150.92,240.49) --
	(151.02,241.67) --
	(151.11,242.85) --
	(151.21,244.03) --
	(151.30,245.21) --
	(151.39,246.39) --
	(151.49,247.56) --
	(151.58,248.74) --
	(151.67,249.92) --
	(151.76,251.10) --
	(151.85,252.28) --
	(151.93,253.46) --
	(152.02,254.64) --
	(152.11,255.81) --
	(152.19,256.99) --
	(152.28,258.17) --
	(152.30,258.51) --
	(152.36,259.35) --
	(152.44,260.53) --
	(152.52,261.71) --
	(152.60,262.89) --
	(152.68,264.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44, 79.62) --
	(299.61, 80.19) --
	(299.50, 80.22) --
	(297.56, 80.85) --
	(295.98, 81.37) --
	(295.62, 81.49) --
	(293.69, 82.15) --
	(292.56, 82.55) --
	(291.75, 82.84) --
	(289.81, 83.55) --
	(289.34, 83.73) --
	(287.88, 84.28) --
	(286.29, 84.91) --
	(285.94, 85.04) --
	(284.00, 85.83) --
	(283.40, 86.08) --
	(282.07, 86.65) --
	(280.65, 87.26) --
	(280.13, 87.49) --
	(278.19, 88.37) --
	(278.05, 88.44) --
	(276.26, 89.28) --
	(275.56, 89.62) --
	(274.32, 90.23) --
	(273.20, 90.80) --
	(272.38, 91.22) --
	(270.94, 91.98) --
	(270.45, 92.24) --
	(268.78, 93.16) --
	(268.51, 93.30) --
	(266.71, 94.33) --
	(266.57, 94.41) --
	(264.73, 95.51) --
	(264.64, 95.57) --
	(262.83, 96.69) --
	(262.70, 96.78) --
	(261.01, 97.87) --
	(260.76, 98.03) --
	(259.26, 99.05) --
	(258.83, 99.35) --
	(257.57,100.23) --
	(256.89,100.72) --
	(255.96,101.41) --
	(254.95,102.16) --
	(254.40,102.59) --
	(253.02,103.67) --
	(252.89,103.76) --
	(251.44,104.94) --
	(251.08,105.24) --
	(250.04,106.12) --
	(249.14,106.90) --
	(248.69,107.30) --
	(247.38,108.48) --
	(247.20,108.64) --
	(246.12,109.66) --
	(245.27,110.47) --
	(244.90,110.84) --
	(243.71,112.02) --
	(243.33,112.40) --
	(242.56,113.19) --
	(241.45,114.37) --
	(241.39,114.44) --
	(240.37,115.55) --
	(239.46,116.58) --
	(239.33,116.73) --
	(238.31,117.91) --
	(237.52,118.85) --
	(237.33,119.09) --
	(236.37,120.27) --
	(235.58,121.26) --
	(235.44,121.44) --
	(234.53,122.62) --
	(233.65,123.80) --
	(233.65,123.80) --
	(232.79,124.98) --
	(231.96,126.16) --
	(231.71,126.51) --
	(231.14,127.34) --
	(230.35,128.52) --
	(229.77,129.39) --
	(229.58,129.70) --
	(228.82,130.87) --
	(228.09,132.05) --
	(227.84,132.47) --
	(227.37,133.23) --
	(226.67,134.41) --
	(225.99,135.59) --
	(225.90,135.75) --
	(225.33,136.77) --
	(224.67,137.95) --
	(224.04,139.12) --
